Comparing fluorometric methods ( in vivo vs extracted) for cyanoHAB monitoring in six Rhode Island ponds

### 2024-02-20 manuscript/manuscript.qmd
switched to cells/ml on Fig 4

Cyanophytes were the dominant taxa by relative biovolume at Curran (0.75), Mashapaug (0.87), and Warwick (0.89); Chrysophytes at Barber (0.39) and Yawgoo (0.44); and Bacillariophytes at Indian (0.41)(@fig-relbv).  Total biovolume concentrations were highest at Mashapaug (2.12x10^7^), Warwick (1.44x10^7^), and Curran (3.22x10^6^)(@fig-bv). Microcystis was the dominant genus at Mashapaug and Warwick, while Chrysosporum was dominant at Curran (@tbl-supp).

![Compare Relative Biovolume of divisions by waterbody](images/fig4_rel_bio_bar.jpg){#fig-relbv width="8.5in" height="5.25in"}

![Compare Total Biovlume of divisions by waterbody](images/fig5_total_bio_bar.jpg){#fig-bv width="8.5in" height="5.25in"}

@@

![Compare fluorometer chlorophyll to cyanobacteria cell counts](images/fig6_chl_vs_cells.jpg){#fig-chlcount width="8.5in" height="5.25in"}

![Compare fluorometer phycocyanin to cyanobacteria cell counts](images/fig7_phyco_vs_cells.jpg){#fig-phycocount width="8.5in" height="5.25in"}

>>>>

!!!REWRITE ME - Changed from biov to cells/ml, only one fig now!!!!

Cyanophytes were the dominant taxa by relative biovolume at Curran (0.75), Mashapaug (0.87), and Warwick (0.89); Chrysophytes at Barber (0.39) and Yawgoo (0.44); and Bacillariophytes at Indian (0.41)(@fig-cellsml).  Total biovolume concentrations were highest at Mashapaug (2.12x10^7^), Warwick (1.44x10^7^), and Curran (3.22x10^6^)(@fig-bv). Microcystis was the dominant genus at Mashapaug and Warwick, while Chrysosporum was dominant at Curran (@tbl-supp).

![Compare Cells/mL of divisions by waterbody](images/fig4_total_cellsml_bar.jpg){#fig-cellsml width="8.5in" height="5.25in"}

@@

![Compare fluorometer chlorophyll to cyanobacteria cell counts](images/fig5_chl_vs_cells.jpg){#fig-chlcount width="8.5in" height="5.25in"}

![Compare fluorometer phycocyanin to cyanobacteria cell counts](images/fig6_phyco_vs_cells.jpg){#fig-phycocount width="8.5in" height="5.25in"}
